Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2019-11-01 code/98-paper/ieee/performance-best-per-learner.tex
save learner results for watching changes

% latex table generated in R 3.5.2 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllr}
  \hline
 & Task & Learner Group & Filter & RMSE \\ 
  \hline
1 & defoliation-all-plots-HR-NRI-VI & XGBoost & Borda & 32.37 \\ 
  2 & defoliation-all-plots-NRI & RF & Car & 33.50 \\ 
  3 & defoliation-all-plots-HR-NRI & SVM & Car & 33.95 \\ 
  4 & defoliation-all-plots-NRI & Ridge-CV & No Filter & 34.05 \\ 
  5 & defoliation-all-plots-HR & Lasso-CV & No Filter & 50.45 \\ 
  6 & defoliation-all-plots-VI & Ridge-MBO & No Filter & 58.55 \\ 
  7 & defoliation-all-plots-HR & Lasso-MBO & No Filter & 58.56 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 3.5.2 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllr}
  \hline
 & Task & Learner Group & Filter & RMSE \\ 
  \hline
1 & defoliation-all-plots-NRI & RF & Car & 33.52 \\ 
  2 & defoliation-all-plots-NRI & XGBoost & Borda & 33.91 \\ 
  3 & defoliation-all-plots-NRI & Ridge-CV & No Filter & 34.05 \\ 
  4 & defoliation-all-plots-HR-VI & SVM & Borda & 34.35 \\ 
  5 & defoliation-all-plots-HR & Lasso-CV & No Filter & 50.45 \\ 
  6 & defoliation-all-plots-HR & Ridge-MBO & No Filter & 58.28 \\ 
  7 & defoliation-all-plots-HR & Lasso-MBO & No Filter & 58.56 \\ 
   \hline
\end{tabular}
}
\end{table}
